---
title: "Managing Ostracode Elements"
format: html
---

```{r read_tables, echo = FALSE}
library(readr)
library(dplyr)
library(httr)
library(jsonlite)

node <- readr::read_csv('NODEdatabase22May2024.csv')
eanode <- readr::read_csv('EANODpublisheddataJune2024.csv')
```

## Table Additions

The following tables need new information to manage the data:

* `ndb.publications` (Publication data)
* `ndb.depenvttypes` (New depositional environments)
* `ndb.lakeparametertypes` (Add lake water type/quality)

## Publications

For publications we will search all publications using CrossRef, and add them if we can find them. Otherwise, we will simply add the citation string.

```{r extract_publications}
unique_pubs <- eanode$bibliographicCitation |> unique()
node_pubs <- c(readr::read_lines('node_publications.txt') |> unique(), unique_pubs)
new_pubs = list()

fetch_url = "https://api.crossref.org/works"
for (i in unique_pubs) {
    cross_result <- httr::GET(url = fetch_url, query=list(query=i), 
        httr::add_headers(`User-Agent`="NeotomaDataScraper;mailto:goring@wisc.edu"))
    data <- content(cross_result)['message'][[1]]
    scores <- sapply(data$items, function(j){j$score})
    if (diff(scores)[1] < diff(scores)[2] * 10) {
        ref = data$items[1]
        new_pubs[[length(new_pubs) + 1]] <- list(citation = i,
                                                 json = toJSON(ref[[1]]),
                                                 doi = ref[[1]]$DOI)
        cat("Positive hit for pub.\n")
    } else {
        new_pubs[[length(new_pubs) + 1]] <- list(citation = i,
                                                 json = NA)
    }
}

```

## Lake Parameters

We need to add the following critical `lakeparametertypes` to Neotoma. We need to account for the values "Lentic", "lotic", Subterranean", and "estuarine".

```{sql}
INSERT INTO ndb.lakeparametertypes (lakeparametershortname, lakeparameter)
VALUES('AquaticSystem', 'Aquatic System');

```

## Depositional Environments

We need to check the following parameters against Neotoma:

```{r depositionalenvts}
habitats <- c(eanode$habitat, node$`NATURAL HABITAT`, node$`ARTIFICIAL HABITAT`) |> 
    unique() |>
    na.omit() |>
    write.csv('habitat_equiv.csv')

```